\documentclass{rahul_cv}

\setname{Rahul Singh}{Satbir}{Parmar}
\setaddress{Mumbai/India}
\setmobile{+91 9619896014}
\setwebsite{\href{https://rahulsinghparmar.me/}{rahulsinghparmar.me}}
\setmail{rahulsinghparmar4@protonmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/rahul-singh-2b27211a7/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/RahulSinghParmar} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables}
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Career Vision}{%
I am committed to building a successful career with an organization that provides opportunities to apply my theoretical, logical, and technical skills in a practical, real-world environment. I thrive in collaborative environments with dedicated and passionate team members, where I can challenge myself and continuously learn and grow. As a key player, I am eager to contribute to creative and challenging projects and leverage my potential to achieve both personal and organizational success.
%As a recent graduate in computer science with a focus on full-stack development, I am excited to start my career as a Java full stack developer. I have completed several projects that involve creating interactive web applications using various web development frameworks and tools. I have experience with front-end technologies like HTML, CSS, and JavaScript, and have worked with databases and deployed applications on cloud platforms. I am a quick learner and enjoy collaborating with cross-functional teams to deliver high-quality products. I am excited to contribute to challenging projects and continue to learn and grow as a developer.

}
%
%Education
\section{Education} 
    \datedexperience{Thakur College of Engineering And Technology}{Aug. 2016 – July. 2021} 
    \explanation{B.E in Computer Engineering} %
     \explanationdetail{\coloredbullet\ % 
     I earned a degree in computer engineering from TCET/Mumbai University, where I gained a strong foundation in computer programming, algorithms, data structures, and computer architecture.
     %\lipsum[1][3-4]\par %replace this part with actual text
     }
    \datedexperience{Thakur Vidya Mandir Jr College}{May. 2014 – Feb. 2016} 
    \explanation{HSC in Science} %
    \explanationdetail{\coloredbullet\ %
     %\lipsum[1][3-4]\par %replace this part with actual text
     I completed my high school education at TVM, where I received a comprehensive education in various subjects, including mathematics, physics, chemistry, computer hardware and software, English, and communication skills.
     }
%
% Experience
% \section{Experience}
%     %
%     \datedexperience{Intertech Inc.}{2014-Summer / Turkey} 
%     \explanation{Intern as android developer} 
%     %
%     \datedexperience{Velocity Inc.}{2015-Summer / Turkey} 
%     \explanation{Intern as Developer/Tester} 
%     %
%     \datedexperience{Akbank}{2018-2019 / Turkey} 
%     \explanation{Ios Developer} 
%     \explanationdetail{\coloredbullet\ %
%      \lipsum[1][1-2]\par %replace this part with actual text
%      }
%     %
%     \datedexperience{Mobile-Software AG}{2019-2020 / Germany} 
%     \explanation{Ios Developer} 
%     \explanationdetail{\coloredbullet\ %
%      \lipsum[1][4-5]\par %replace this part with actual text
%      }
%     %
%     \datedexperience{BMW Autonomous Driving Campus}{2020-Now / Germany} 
%     \explanation{Working Student} 
%     \explanationdetail{\coloredbullet\ %
%      \lipsum[1][3-4]\par %replace this part with actual text
%      }
% %

%
%Project
\section{Projects} 
    \newcommand{\skillsix}{\createskill{Predictive System for Heart Disease:}
    {\emph{Diagnosis of Heart Disease Using Data Mining Algorithms.}}
    }
    \newcommand{\skillseven}{\createskill{Endless Runner Game:}
    {\emph{A fun game made using unity based on concept of game \href{https://play.google.com/store/apps/details?id=com.rahulsinghparmar}{‘Zig-Zag’}.}}
    }
    \newcommand{\skilleight}{\createskill{Java-Core Programmings:}
    {\emph{Open Source from basic \href{https://github.com/RahulSinghParmar/JAVA-Core}{java-core} Programming and OOPS concept.}}
    }
    \newcommand{\skillnine}{\createskill{CustomPCBuilder:}
    {\emph{A simple java application to build \href{https://github.com/RahulSinghParmar/CustomPcBuild}{custom PC} using basic OOPs operation.}}
    }
    
    %
    \createskills{\skillsix, \skillseven, \skilleight, \skillnine}
%
% Technical Skills
\section{Technical Skills}
    %
    \textbf{\explanation{CORE  JAVA} }
    \explanationdetail{ %
     %\lipsum[1][3-4]\par %replace this part with actual text
           \coloredbullet\ Very strong knowledge on \textbf{\emph{OOPS}} concepts like \textbf{\emph{Method overloading}} and \textbf{\emph{Method overriding}}. %
        \\ \coloredbullet\ Good knowledge on \textbf{\emph{Inheritance}}, \textbf{\emph{Polymorphism}}. %
        \\ \coloredbullet\ Having good knowledge on \textbf{\emph{Abstraction}} and \textbf{\emph{Encapsulation}}.
        \\ \coloredbullet\ Strong knowledge on \textbf{\emph{up casting}} and \textbf{\emph{down casting}}.
        \\ \coloredbullet\ Very good knowledge on \textbf{\emph{constructors}} and \textbf{\emph{interface}}.
        \\ \coloredbullet\ Good practical knowledge on \textbf{\emph{Collection Frameworks}} like \emph{List, Queue and Set}. 
        \\ \coloredbullet\ Good in \textbf{\emph{Exception Handling}} and written many custom Exceptions.
        \\ \coloredbullet\ Having basic Knowledge on \textbf{\emph{threads}}
    }
    %
    \textbf{\explanation{JDBC} }
    \explanationdetail{ %
     %\lipsum[1][3-4]\par %replace this part with actual text
           \coloredbullet\ Good Architectural understanding of JDBC and \textbf{\emph{Loose coupling}}.
        \\ \coloredbullet\ Implemented all types of statements like \textbf{\emph{Statement,Prepared Statements and Callable Statements}}.
        \\ \coloredbullet\ Implemented JDBC \textbf{\emph{CRUD}} operations.
        \\ \coloredbullet\ Used \textbf{\emph{configuration files}} and implemented best practices.
    }
    %
    \textbf{\explanation{SERVLET} }
    \explanationdetail{ %
     %\lipsum[1][3-4]\par %replace this part with actual text
           \coloredbullet\ Possessing good knowledge in servlets and \textbf{\emph{server side}} programmings .
        \\ \coloredbullet\ Possessing good knowledge of \textbf{\emph{JSP}}.
        \\ \coloredbullet\ Depth understanding of \textbf{\emph{Servlet and JSP implicit }}objects.
    }
    % 
    \textbf{\explanation{SQL} }
    \explanationdetail{ %
     %\lipsum[1][3-4]\par %replace this part with actual text
           \coloredbullet\   Good understanding of \textbf{\emph{RDBMS}} concepts.
        \\ \coloredbullet\   Exposure to \textbf{\emph{constraints}} (PK, FK, NOTNULL, UNQ, CHECK).
        \\ \coloredbullet\   Ability to write queries using \textbf{\emph{joins, sub queries, grouping}} etc.
        \\ \coloredbullet\   Knowledge of \textbf{\emph{DDL, DML, TCL}}.
    }     
%
% PERSONAL STRENGTH 
\section{Personal Strength}
    %
    \textbf{\explanation{Attention to detail}} 
    \explanationdetail{\coloredbullet\ %
     Skilled at catching errors during code review and testing, improving code quality and functionality.
     }
    %
    \textbf{\explanation{Problem-solving}}
    \explanationdetail{\coloredbullet\ %
     Proven ability to analyze complex problems, develop innovative solutions, and effectively troubleshoot issues, \\ resulting in increased efficiency and functionality of software systems.
     }
     %
    \textbf{\explanation{Privacy and Security-focused Technologist}}
    \explanationdetail{\coloredbullet\ %
     Deep commitment to ensuring the privacy and security of user data through a comprehensive understanding of best practices and emerging trends in privacy and security technologies.
     }
     %
    \textbf{\explanation{Fast learner}}
    \explanationdetail{\coloredbullet\ %
     Quick learner who easily adapts to new programming languages, frameworks, and development tools, keeping up-to-date with industry trends and techniques.
     }
     %
    \textbf{\explanation{Strong analytical skills}}
    \explanationdetail{\coloredbullet\ %
     Strong analytical skills, developing efficient and effective software solutions that exceed client expectations.
     }
     %
    \textbf{\explanation{Time management}}
    \explanationdetail{\coloredbullet\ %
     Effective time manager who consistently meets project deadlines by prioritizing tasks and communicating project status updates.
     }
     %
    \textbf{\explanation{Passionate about technology}}
    \explanationdetail{\coloredbullet\ %
     Passionate about technology and software development, seeking new challenges and opportunities for \\ professional growth and development.
     }

% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  JAVA \cpshalf SQL \cpshalf J2EE \ \ \textbf{\emph{Familiar:}} \ \  Python \cpshalf JavaScript \cpshalf HTML \cpshalf CSS \cpshalf XML}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{ My-SQL and Oracle DBMS \cpshalf GIT \cpshalf CLI \cpshalf JDBC \cpshalf Jakarta EE} \cpshalf Servlet \cpshalf JSPs \cpshalf Maven} % Programming Paradigms
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Spring Framework \cpshalf Hibernate \cpshalf Apache Tomcat \cpshalf Java Servlet API \cpshalf MySQL Connector/J }} % \cpshalf Pandas \cpshalf Scikit-learn \cpshalf Gym \cpshalf PyTorch \cpshalf Tensorflow
    % %
    % \newcommand{\skillfour}{\createskill{iOS Programming}{RxSwift \cpshalf PromiseKit \cpshalf CocoaPods \cpshalf Autolayout/DSLs}}
    %
    \newcommand{\skillfour}{\createskill{Design Patterns}{ Singleton \cpshalf MVC \cpshalf DTO \cpshalf DAO } \cpshalf Factory Pattern } % Singleton, Model View Controller (MVC), Data Transfer Object (DTO), Data Access Object (DAO), and Factory Pattern
    %
    \newcommand{\skillfive}{\createskill{Technologies}{ RDP \cpshalf AWS ec2 \cpshalf GitHub  \cpshalf Network Administration \cpshalf VirtualBox }}
    %
    \newcommand{\skilleleven}{\createskill{OS}{ Windows Server \cpshalf RHEL \cpshalf MacOS \cpshalf Debian \cpshalf Ubuntu }}
    %
    \newcommand{\skilltwelve}{\createskill{Tools \ \& \ IDE's}{ Vim \cpshalf IntelliJ IDEA \cpshalf Eclipse \cpshalf VScode \cpshalf MySql WorkBench \cpshalf Oracle 10g \cpshalf Unity Engine }}
    %
    \newcommand{\skillten}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Hindi \ \ \textbf{\emph{Fluent:}} \ \ English  }} %\ \ \textbf{\emph{Beginner:}} \ \  German
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive, \skilleleven, \skilltwelve, \skillten}
% 
% Experience
% \section{Extra}
%     \newcommand{\extraone}{%
%     \lipsum[1][7-8]\par %replace this part with actual text
%     }
%     %
%     \newcommand{\extratwo}{%
%     \lipsum[1][9-10]\par %replace this part with actual text
%     }
%     %
%     \newcommand{\extrathree}{%
%     \lipsum[1][11-12]%replace this part with actual text
%     }
%     %
%     \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
%     %
%     \createbullets{\listofextras}
%
% Hobbies
\section{Hobbies}
    \newcommand{\extraone}{%
    \textbf{Open source contributions} - Contributing to open source projects to improve my coding skills and give back.
    }
    %
    \newcommand{\extratwo}{%
    \textbf{Gaming} - Playing video games as a way to relax, and potentially learn more about game development and design.
    }
    %
    \newcommand{\extrathree}{%
    \textbf{Fitness} - Engaging in physical activities to maintain physical and mental health.
    }
    %
    \newcommand{\extrafour}{%
    \textbf{Sports} - Participating in team or individual sports as a way to stay active and build social connections.
    }
    %
    \newcommand{\extrafive}{%
    \textbf{Painting or drawing} - Creating art as a way to express myself and develop my creativity.
    }
    %
    \newcommand{\extrasix}{%
    \textbf{Practicing online anonymity} - Exploring anonymity through VPNs, Tor browsers, and encrypted messaging apps to protect personal information.
    }
    %
    \newcommand{\extraseven}{%
    \textbf{Exploring emerging technologies} - Keeping up with emerging technologies through reading, following \\ influence's, attending events, and experimenting with new tools.
    }
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree, \extrafour, \extrafive , \extrasix, \extraseven }
    %
    \createbullets{\listofextras}

%Footnote
\createfootnote
\end{document}
